signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-17 paper.tex
fixed dangerous bug in results_analysis

%model structure
\begin{figure}
 \begin{minipage}{.5\linewidth} 
 \caption{Scheme of signalHsmm}
     \resizebox{6.5cm}{!}{%
    \begin{tikzpicture}[->,>=stealth',shorten >=2pt,auto,node distance=4.5cm, thick]
    \label{fig:model_hsmm}
      \tikzstyle{line} = [draw=black, color=blue!30!black!50, line width=4.5mm, -latex']
      \tikzstyle{main node} = [circle,fill=blue!20,draw, minimum size = 2.2cm, font=\itshape,
         align=center,  top color=white, bottom color=blue!50!black!70 ] %font=\sffamily\small\bfseries,
      %nodes
      \node[main node]            (start') 	[]						{Start};	     
      \node[main node, bottom color=purple!70!black!70] 	(nregion') 	[right of=start',xshift=-5mm, yshift=15mm] 	{n-region};
      \node[main node, bottom color=pink!70!black!70] 	(hregion') 	[right of=nregion',xshift=-5mm,yshift=15mm] 	{h-region};
      \node[main node, bottom color=gray!70!black!70] 	(cregion') 	[right of=hregion',xshift=-5mm,yshift=-15mm] 	{c-region};
      \node[main node, bottom color=green!70!black!70] 	(mature') 	[right of=cregion',xshift=-5mm, yshift=-15mm] 	{Mature protein};

      %lines
      \path [line] (start')   edge node [left, color=black] {} (nregion');
      \path [line] (nregion') edge node [below, color=black] { } (hregion');
      \path [line] (hregion') edge node [below, color=black] { } (cregion');
      \path [line] (cregion') edge node [left, color=black] { } (mature');
      \draw [line] (start') to[out=340,in=200] (mature');
    \end{tikzpicture} }
\end{minipage}
 \begin{minipage}{.5\linewidth}
   \caption{Scheme of signalHsmm with cleavage site motives}
     \resizebox{6.5cm}{!}{%
    \begin{tikzpicture}[->,>=stealth',shorten >=2pt,auto,node distance=4.5cm, thick]
    \label{fig:model_hsmm_kMer}
      \tikzstyle{line} = [draw=black, color=blue!30!black!50, line width=4.5mm, -latex']
      \tikzstyle{main node} = [circle,fill=blue!20,draw, minimum size = 2.2cm, font=\itshape,
         align=center,  top color=white, bottom color=blue!50!black!70 ] %font=\sffamily\small\bfseries,
      %nodes
      \node[main node]            (start')   []  					{Start};	     
      \node[main node, bottom color=purple!70!black!70] 	(nregion') 	[right of=start',xshift=-25mm, yshift=35mm] 	{n-region};
      \node[main node, bottom color=pink!70!black!70] 	(hregion') 	[right of=nregion',xshift=-25mm,yshift=35mm] 	{h-region};
      \node[main node, bottom color=gray!70!black!70] 	(cregion') 	[right of=hregion',xshift=-10mm,yshift=-25mm] 	{c-region};
      \node[main node, bottom color=green!70!black!70] 	(mature') 	[below of=hregion',xshift=15mm, yshift=-90mm] 	{Mature protein};

@@

      %\draw [decorate,line width=3pt,decoration={brace,amplitude=10pt}] ([xshift=5mm, yshift=5mm]kmer1) -- ([yshift=-25mm]kmer3) node [black,midway,xshift=0.6cm] {\footnotesize $P_1$};
      \draw[decoration={brace,amplitude=10pt, raise=5pt},decorate, line width=2pt]  
      ([yshift=1mm]kmer1.east) -- ([yshift=-5mm]kmer3.east) node [black,midway,xshift=0.6cm] {\large \color{yellow!50!black!90} k-mer};
    \end{tikzpicture} }
    \end{minipage}
\end{figure}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/cvres.png}
\caption{Results of cross-validation. 1. An encoding providing the best sensitivity (AUC = 0.9337). 2. A group of encodings with be best sensitivity/specificity ratio (mean AUC = 0.9650). 3. An encoding providing the best specificity (AUC = 0.9686).}
\label{fig:cvres}
\end{figure}

>>>>

%model structure
\begin{figure}
 \begin{minipage}{.5\linewidth} 
     \resizebox{6.5cm}{!}{%
    \begin{tikzpicture}[->,>=stealth',shorten >=2pt,auto,node distance=4.5cm, thick]
    \label{fig:model_hsmm}
      \tikzstyle{line} = [draw=black, color=blue!30!black!50, line width=4.5mm, -latex']
      \tikzstyle{main node} = [circle,fill=blue!20,draw, minimum size = 2.2cm, font=\itshape,
         align=center,  top color=white, bottom color=blue!50!black!70 ] %font=\sffamily\small\bfseries,
      %nodes
      \node[main node]            (start') 	[]						{Start};	     
      \node[main node, bottom color=purple!70!black!70] 	(nregion') 	[right of=start',xshift=-5mm, yshift=15mm] 	{n-region};
      \node[main node, bottom color=pink!70!black!70] 	(hregion') 	[right of=nregion',xshift=-5mm,yshift=15mm] 	{h-region};
      \node[main node, bottom color=gray!70!black!70] 	(cregion') 	[right of=hregion',xshift=-5mm,yshift=-15mm] 	{c-region};
      \node[main node, bottom color=green!70!black!70] 	(mature') 	[right of=cregion',xshift=-5mm, yshift=-15mm] 	{Mature protein};

      %lines
      \path [line] (start')   edge node [left, color=black] {} (nregion');
      \path [line] (nregion') edge node [below, color=black] { } (hregion');
      \path [line] (hregion') edge node [below, color=black] { } (cregion');
      \path [line] (cregion') edge node [left, color=black] { } (mature');
      \draw [line] (start') to[out=340,in=200] (mature');
    \end{tikzpicture} }
    \caption{The diagram of signalHsmm.}
    \label{fig:signalHsmm}
\end{minipage}
 \begin{minipage}{.5\linewidth}
     \resizebox{6.5cm}{!}{%
    \begin{tikzpicture}[->,>=stealth',shorten >=2pt,auto,node distance=4.5cm, thick]
    \label{fig:model_hsmm_kMer}
      \tikzstyle{line} = [draw=black, color=blue!30!black!50, line width=4.5mm, -latex']
      \tikzstyle{main node} = [circle,fill=blue!20,draw, minimum size = 2.2cm, font=\itshape,
         align=center,  top color=white, bottom color=blue!50!black!70 ] %font=\sffamily\small\bfseries,
      %nodes
      \node[main node]            (start')   []  					{Start};	     
      \node[main node, bottom color=purple!70!black!70] 	(nregion') 	[right of=start',xshift=-25mm, yshift=35mm] 	{n-region};
      \node[main node, bottom color=pink!70!black!70] 	(hregion') 	[right of=nregion',xshift=-25mm,yshift=35mm] 	{h-region};
      \node[main node, bottom color=gray!70!black!70] 	(cregion') 	[right of=hregion',xshift=-10mm,yshift=-25mm] 	{c-region};
      \node[main node, bottom color=green!70!black!70] 	(mature') 	[below of=hregion',xshift=15mm, yshift=-90mm] 	{Mature protein};

@@

      %\draw [decorate,line width=3pt,decoration={brace,amplitude=10pt}] ([xshift=5mm, yshift=5mm]kmer1) -- ([yshift=-25mm]kmer3) node [black,midway,xshift=0.6cm] {\footnotesize $P_1$};
      \draw[decoration={brace,amplitude=10pt, raise=5pt},decorate, line width=2pt]  
      ([yshift=1mm]kmer1.east) -- ([yshift=-5mm]kmer3.east) node [black,midway,xshift=0.6cm] {\large \color{yellow!50!black!90} k-mer};
    \end{tikzpicture} }
    \caption{Scheme of signalHsmm extended wtich the n-gram cleavage site model.}
    \label{fig:ngramext}
    \end{minipage}
\end{figure}

@@

\subsection*{Cross-validation}

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/cvres.png}
\caption{}
\label{fig:cvres}
\end{figure}
